---
title: "ELT Study"
runtime: shiny
#output: html_document
output: 
    flexdashboard::flex_dashboard:
           vertical_layout: scroll
           orientation: rows
---

```{r, echo = FALSE}
library(flexdashboard)
library(highcharter)
#library(devtools)
library(shiny)
library(DT) ## tem que vir depois do shiny
library(dplyr)
library(readr)
#path <<- renderText({input$file1$datapath})
```

Loading Data {data-orientation=rows}
=====================================

Row {data-height=100}
-------------------------------------

```{r}
 fileInput('file1', 'Choose CSV File',
   accept=c('text/csv',
     'text/comma-separated-values,text/plain',
     '.csv'))

#plotOutput("eltp", height = "100%")


elt <- reactive({
    inFile <- input$file1
    if (is.null(inFile)) return(NULL)
   data <- read.csv2(inFile$datapath)
   df <- data %>% mutate(EE = PERSPVALUE / EXPVALUE) %>% arrange(desc(EE))
   df
})  
```


Row 
-------------------------------------

### ELT

 All the information needed to generate the EP curves is stored in the ELT.
We will assume that this ELT corresponds to the Ground Up financial perspective. 

 Here we add to the ELT the field (EE) with the percentage given by the Loss generated per Event over the Exposure. And then sort the table by this field.

```{r message=FALSE, echo=FALSE, comment = NA }
DT::renderDataTable({
   #validate(
   #   need(!is.null(elt()), "deddededed"
  #         )
  req(elt())   
  DT::datatable(elt(), 
                options = list(pageLength = 5,
    initComplete = JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",
    "}")
    ),
    rownames= FALSE                                 
  ) %>% formatCurrency(c(3:6)," " , mark = " ",digits = 0) %>%
    formatCurrency(7," " , mark = ".",digits = 5) %>%
    formatRound('RATE', 10)
})

 
#reactive({ 
  
#dataTableOutput("table")
```

Dashboards {data-orientation=Row}
=====================================

Row {data-height=400}
-------------------------------------

### Exposure vesus Expected Loss

 Here we show the top 10 most damageable Events.

###

```{r}
#highchartOutput("hcontainer",height = "500px")
  renderHighchart({
  validate(
      need(elt() != "", "Please upload a CSV file")
    )   
#    validate(need(elt(),"Dataframe not found"))
elto <- elt() %>% arrange(desc(EE)) %>% head(n=10) %>% arrange(PERSPVALUE)

hc <- highchart() %>% 
  hc_xAxis(categories = elto$EVENTID,
           title = list(text =  "Event")
           #name = "Event"
           ) %>%   
  
  hc_add_series(#title = list(text =  "ExpectedLoss")
                name = "ExpectedLoss",
                data = elto$PERSPVALUE
                ) %>%
  
  hc_add_series(#title = list(text =  "Exposure"),
                name = "Exposure",
                data = elto$EXPVALUE
                #labels=list(format="{value:,.0f}")
                )   %>%
  
#hc_tooltip(pointFormat = '<span style="color:{series.color}">{series.name}</span>:
#           {point.x:,.0f}   {point.y:,.0f}<br/>') 
                     
#this.series.name
 hc_tooltip(formatter = JS("function(){return (
'<b>Event ID </b>: ' + this.x + '<br> <b>' + this.series.name + '</b>: '+ Highcharts.numberFormat(this.y, 0, '.', ' '))}"))

#        'Serie ' + this.series.name +   
#       'Exposure:  ' + Highcharts.numberFormat(this.x, 0, '.', ' ')  + 
# ' <br> ExpectedLoss: ' + Highcharts.numberFormat(this.y, 0, '.', ' '))
  
  
hc <- hc %>% 
  hc_chart(type = "column",
           options3d = list(enabled = TRUE, beta = 15, alpha = 15))
hc %>% 
  hc_chart(borderColor = '#EBBA95',
           borderRadius = 10,
           borderWidth = 2,
           backgroundColor = list(
             linearGradient = c(0, 0, 500, 500),
             stops = list(
               list(0, 'rgb(255, 255, 255)'),
               list(1, 'rgb(200, 200, 255)')
             )))
})
```

Row {data-height=30}
-------------------------------------

*** 
Please click on the Render Return Periods Table button to see the Return Periods table and the EP curve.


Row 
-------------------------------------

### Return Periods

Return Period Losses are very valuable measures of risk when a single point
on the curve is of importance. Three of the applications of this risk measure
are: 

1. Reinsurance analysis

2. Rating agency reporting

3. Primary layer analysis: Similar to a reinsurance analysis, you can use
return period losses to understand the probabilities associated with
activating or exhausting a policy layer.


```{r}
bootstrapPage(actionButton("rpfBtn", "Render Return Periods Table", class="btn-default"))
```


```{r message=FALSE, echo=FALSE, comment = NA}
rpf <- eventReactive(input$rpfBtn, { 
   
if (is.null(elt())) return(NULL)
  
 l <- sum(elt()$RATE)

tq <- quantile(elt()$PERSPVALUE, c(.05,0.1,0.2,0.4,0.6,0.8, 0.95))

tr <- seq(min(elt()$PERSPVALUE), tq[[1]], (tq[[1]]-min(elt()$PERSPVALUE))/5)
tr1 <- seq(tq[[1]], tq[[2]], (tq[[2]]-tq[[1]])/8)
tr2 <- seq(tq[[2]], tq[[3]], (tq[[3]]-tq[[2]])/8)
tr3 <- seq(tq[[3]], tq[[4]], (tq[[4]]-tq[[3]])/8)
tr4 <- seq(tq[[4]], tq[[5]], (tq[[5]]-tq[[4]])/8)
tr5 <- seq(tq[[5]], tq[[6]], (tq[[6]]-tq[[5]])/8)
tr6 <- seq(tq[[6]], tq[[7]], (tq[[7]]-tq[[6]])/8)
tr7 <- seq(tq[[7]], max(elt()$PERSPVALUE), (max(elt()$PERSPVALUE)-tq[[7]])/110)

#tr <-  seq(min(elt()$PERSPVALUE)+1, max(elt()$PERSPVALUE), #(max(elt()$PERSPVALUE)-min(elt()$PERSPVALUE)+1)/1000)
#thresholds <- c(tr)
#thresholds <- seq(1, max(elt()$PERSPVALUE), (max(elt()$PERSPVALUE))/20)  

thresholds <- c(tr,tr1,tr2,tr3,tr4,tr5,tr6,tr7)

thresholds <- as.data.frame(thresholds)

eltc <- elt() %>% mutate(mu    = PERSPVALUE / EXPVALUE, 
                         sigma = (STDDEVI+STDDEVC)/EXPVALUE,
                         alpha = ((1 - mu) / sigma^2 - 1 / mu) * mu ^ 2,
                         beta  =  alpha * (1 / mu - 1)
)

pr <- as.numeric()
cep <- as.numeric()
oep <- as.numeric()

for(i in 1:nrow(thresholds)){
  for(j in 1:nrow(eltc)){
    pr[j]  <- 1 - pbeta(thresholds[i,]/eltc$EXPVALUE[j], eltc$alpha[j],
                        # pr[j]  <- 1 - pbeta(1/thresholds[i,], eltc$alpha[j],
                        eltc$beta[j]) 
  }
  cep[i] <- sum(eltc$RATE * pr) / sum(eltc$RATE) 
  oep[i] <- 1 - exp(-l*cep[i])
}
oepdf <- data.frame(thresholds=round(thresholds[,1],0),oep)

return(oepdf)

  })
```

###

```{r message=FALSE, echo=FALSE, comment = NA }

DT::renderDataTable({
  req(rpf())   
  
newdataoep <- data.frame(oep =c(0.001, 0.002, 0.004, 0.005, 0.01, 0.02,
                                0.04,0.1,0.2,0.5))


returnPeriod <- 1/newdataoep

rp0 <- approx(rpf()$oep,rpf()$thresholds, xout = newdataoep$oep, method = "linear")

rp <- data.frame( rp0[[1]],
                  returnPeriod,
                  rp0[[2]])    
colnames(rp) <- c("Critical Prob.",
                  "Return Period",
                 "OEP" )  

  DT::datatable(rp, 
                options = list(pageLength = 10,
                               dom = 't',
    initComplete = JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",
    "}")
    ),
    rownames= FALSE
  ) %>% formatPercentage(1,digits = 2) %>%
    formatCurrency(2," " , mark = " ",digits = 0) %>%
    formatCurrency(3," " , mark = " ",digits = 0)

})
 
#reactive({ 
  
#dataTableOutput("table")
```

Row
-------------------------------------

### Average Annual Loss (AAL), Standard Deviation (SD) and Coefficient of Variation

ALL - Expected value of the annual aggregate losses. Measures the overall catastrophe risk, which includes both the frequency and severity of the events

SD - Measure of the volatility in the annual aggregate losses. Incorporates primary and secondary uncertainty from all events in the ELT

CV - SD / AAL

###

```{r}

DT::renderDataTable({
  req(elt())   

AAL <- sum(elt()$PERSPVALUE*elt()$RATE)
SD <- sqrt(sum((elt()$STDDEVI + elt()$STDDEVC)^2))
CV <- SD/AAL

dfAllSd <- data.frame(AAL,
                      SD,
                      CV
                     )


colnames(dfAllSd) <- c("AAL","SD", "CV")
  
   DT::datatable(dfAllSd, 
                options = list(dom = 't',
    initComplete = JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",
    "}")
    ),
    rownames= FALSE
  ) %>% formatCurrency(1," " , mark = " ",digits = 0) %>%
         formatCurrency(2," " , mark = " ",digits = 0) %>%
         formatCurrency(3," " , mark = " ",digits = 5) 

})

```


Row 
-------------------------------------

### Add a different OEP

```{r}
#textInput("oep", "OEP:", "Value here")
#bootstrapPage(actionButton("oepInsert", "OEP", class="btn-default"))
   #   sliderInput("n", "N:", min = 10, max = 1000, value = 200,
    #              step = 10)
      numericInput("oep", "OEP:", "Value here")
#      submitButton("Submit")
bootstrapPage(actionButton("Submit", "Submit", class="btn-default"))

    
```

###

```{r}
p <- eventReactive(input$Submit, {
  validate(need(input$Submit > 0,"Please upload a CSV file and click on the Render EP Curve button"))  
oepr2 <- data.frame(thresholds=round(rpf()$thresholds,0),
                    oep = rpf()$oep)

newoep <- data.frame(c(input$oep))

returnPeriodnew <- data.frame(c(1/newoep))

ap <- approx( oepr2$oep,oepr2$thresholds,
          xout = newoep, 
          method = "linear") 
  #rnorm(input$oep)
nrp <- data.frame( newoep,
            returnPeriodnew,
            OEP = ap[[2]])
colnames(nrp) <- c("Critical Prob.",
                  "Return Period",
                 "OEP" )
nrp
})


DT::renderDataTable({
  req(p())   

  DT::datatable(p(), 
                options = list(pageLength = 10,
                               dom = 't',
    initComplete = JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",
    "}")
    ),
    rownames= FALSE
  ) %>% formatPercentage(1,digits = 2) %>%
    formatCurrency(2," " , mark = " ",digits = 0) %>%
    formatCurrency(3," " , mark = " ",digits = 0)

})
```

Row {data-height=400}
-------------------------------------

### OEP curve
 The Occurrence exceedance probability (OEP) curve shows the probability that the losses for at least one occurrence will exceed a threshold.

 Since the OEP curve is the cumulative distribution for the largest occurrence in a year, it can be used to analyze occurrence-based situations. 
 
 For example, we can calculate the probability of activating and exhausting occurrence-based contracts such as a policy or reinsurance treaty from OEP curves. In addition, the OEP curve can provide statistical information on single event covers.


```{r}
#bootstrapPage(actionButton("EPcurve", "Render EP Curve", class="btn-default"))
```

###

```{r results='asis', message=FALSE, echo=FALSE, comment = NA}
hc <- eventReactive(input$rpfBtn, { 

#oepf   <- rpf()[sort(sample(nrow(rpf()),20)),]

    hc <- hchart(rpf(),"spline",x = thresholds,y = oep*100) %>% 
      hc_xAxis(title = list(text =  "Loss Amout"),
           categories = rpf()$thresholds,
           tickInterval = 100000000,
           labels=list(format="{value:,.0f}")
         )    %>%  
        hc_yAxis(title = list(text =  "Occurrence Exceedance Probability"),
           labels = list(format = "{value}%"),
           max =100,
           tickInterval = 20
             ) %>%   
  hc_tooltip(formatter = JS("function(){
                            return ('Thresholds:  ' + 
      Highcharts.numberFormat(this.x, 0, '.', ' ')  +
                            ' <br> OEP: ' +
                            Highcharts.numberFormat(this.y,2) + '%' )}"))
  
})

renderHighchart({

#validate(need(input$rpfBtn > 0,"Please upload a CSV file and click on the Render #Return Periods Table"))  

 hc() %>% 
  hc_chart(borderColor = '#EBBA95',
           borderRadius = 10,
           borderWidth = 2,
           #height = 600,
           #width = 300,
           backgroundColor = list(
             linearGradient = c(0, 0, 500, 500),
             stops = list(
               list(0, 'rgb(255, 255, 255)'),
               list(1, 'rgb(200, 200, 255)')
             )))
  


 })
```   

